A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-23 colt-21/cvx-flats.tex
edits in appendix

\begin{definition}[Flat]\label{def:flat-general}
	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.

\end{definition}

@@

\begin{lemma}
	  \label{thm:convex-flats-inf-dim}
	Let $\Gamma\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		Let $\Gamma := \prop{L}$.
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

		\emph{Finite $\Y$: }
		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{Simplified prev line}.

		\emph{Infinite $\Y$: }	
		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s. in } p\}$.
		%\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result. (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction, we know it is a $d$-flat.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\subsection{Coping with links for elicitable set-valued properties}
A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
\begin{lemma}\label{lem:intersect-levelsets}
	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{lemma}
\begin{proof}
	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
	Let $\ell$ elicit $\gamma$.
	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
	Let $H = \{ q : v \cdot q = 0 \}$.
	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.

	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{proof}

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
  \end{enumerate}
\end{lemma}
\begin{proof}

	(i)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, we claim $q_\alpha \in F$.
	Observe $p \in F \implies \E_p V(Y) = \vec 0$, and $q \in F \implies \E_q V(Y) = \vec 0$.
	By linearity of expectation, we then have $\E_{q_\alpha} V(Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
	This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

	\bigskip

	(ii)
	Let $p \in F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-flat.)
	We aim to show $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$.

	The first equality follows if we show $\spn(F_p) = \ker(T_W)$.
	Let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
	As $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ as a Corollary of (i), there must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}

	Now, $\dim(\ker(T_W)) \geq \dim(\spn(P_p)) - d$ follows from the rank nullity theorem, as $\P$ is defined as a set of probability distributions over a finite outcome set $\Y$.
	The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
	As $\dim(\im(T_W)) \geq d$, this yields the desired inequality.

	Chaining the results together yields $\dim(\spn(F_p)) \geq \dim(\spn(\P_p)) - d$.

%	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
%	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
%	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
%	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
%	
%	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
%	
%	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
%	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
%	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
%	
%	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

\begin{lemma}\label{lem:Fp-subset-feasible-subset}
Suppose we are given $p \in \relint{P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
\end{lemma}
\begin{proof}
	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}; this flat $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	By~\ref{lem:finite-relint-dim} (i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
	Consider $v \in F_p$.
	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

@@

Suppose $F \subseteq \gamma_r$.
We show $F \subseteq \gamma_{r'}$.
Let $q \in F$.
Since, by Lemma~\ref{lem:finite-relint-dim} (i), we have $p \in \relint{F}$, there is a $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$

>>>>

\begin{definition}[Flat]\label{def:flat-general}
  For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat}, is a nonempty set $F = \zeros{W} := \{q \in \P : \E_q W = \vec 0\}$ for some measurable $W:\Y \to \reals^d$.
\end{definition}

@@

\begin{lemma}
	  \label{thm:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		Let $\Gamma := \prop{L}$.
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

		\emph{Finite $\Y$: }
		If $\Y$ is finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
		Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
		Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$\raft{This is a good place to observe $\E_p V_{u,p} = 0$}.

		\emph{Infinite $\Y$: }	
		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \text{ measurable}, V(y) \in \partial L(u,y) \text{ a.s. in } p\}$.
		%\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result. (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$\raft{I think you're skipping a step or two here, so I'd suggest spelling this out.  You want $\E_p V = 0$ after all, so not any $V$ in that set.}, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.  Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction, we know it is a $d$-flat.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\subsection{Coping with links for elicitable set-valued properties}
A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
\begin{lemma}\label{lem:intersect-levelsets}
	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{lemma}
\begin{proof}
	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
	Let $\ell$ elicit $\gamma$.
	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
	Let $H = \{ q : v \cdot q = 0 \}$.
	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{proof}

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  \raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
    (Such a function must exist by $F$ being a $d$-flat.)}

  (i)
  Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P$\raft{You want the quantification order of $\epsilon$ and $q$ swapped I think; also, add ``for all'' for clarity}, $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
  In particular, for $q \in F$, we claim $q_\alpha \in F$.
  \raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing. Better to do all that before both bullets. ``As $F$ is a $d$-flat, we have some $W$... $F=\zeros{W}$''.  Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
  As $p,q \in F$, we have $\E_pV = \E_qV = \vec 0$.
  By linearity of expectation, we then have $\E_{q_\alpha} V = \vec 0$.
  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

  (ii)
  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
  We first show $\spn(F_p) = \ker(T_W)$.
  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}

  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)}
  % 
  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
  %	
  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
  %	
  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
  %	
  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

\begin{lemma}\label{lem:Fp-subset-feasible-subset}
Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
\end{lemma}
\begin{proof}
	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}\raft{Lemma?}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
	Consider $v \in F_p$.
	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
\end{proof}

@@

Suppose $F \subseteq \gamma_r$; we wish to show $F \subseteq \gamma_{r'}$.
Let $q \in F$.
By Lemma~\ref{lem:finite-relint-dim}(i), we have $p \in \relint{F}$, so there exists $\epsilon > 0$ so that $q' = p - \epsilon (q-p) \in F$.
